Co-citations in context

### 2019-06-14 cocit_r.tex
Minor Revisions

\textcolor{blue}{Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns. Further work might explore additional constraints on random assignment of citations to publications. For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions. Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}

>>>>

Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns. Further work might explore additional constraints on random assignment of citations to publications. For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions. Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
